%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Projects}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Senior Thesis Project} % Class/Purpose
    {EduAttain: A Statistical Analysis of the Impact of Different Demographic Indicators on Educational Attainment} % Title
    {} % Location
    {In Progress} % Date(s)
    {
      \begin{cvitems} % Description(s)
        \item {A data analysis project, using data from IPUMS CPS USA, that will generate a regression and visualizations to show how race, gender, and income relate to educational attainment.}
        \item{\underline{Skills:} R, SQL}
      \end{cvitems}
    }
    
%---------------------------------------------------------
  \cventry
    {Mozilla x Allegheny College CS Dept.} % Class/Purpose
    {GatorMiner} % Title
    {} % Location
    {Aug. 2020 - May 2021} % Date(s)
    {
      \begin{cvitems} % Description(s)
        \item {A visualized text mining and analysis tool for student markdown reflection documents based on Natural Language processing in the Department of Computer Science at Allegheny College.}
        \item{\underline{Skills:} Python, pytest}
      \end{cvitems}
    }
    
%---------------------------------------------------------
  \cventry
    {Selected Class Project} % Class/Purpose
    {ConfiGator} % Title
    {} % Location
    {Feb. 2022} % Date(s)
    {
      \begin{cvitems} % Description(s)
        \item {A configuration file generator meant to be used with GatorGradle.}
        \item{\underline{Skills:} Python, PyPI}
      \end{cvitems}
    }
    
%---------------------------------------------------------
  \cventry
    {Selected Class Project} % Class/Purpose
    {Differences in Rates of Poverty and Spending Based on Gender (in Africa)} % Title
    {} % Location
    {Dec. 2021} % Date(s)
    {
      \begin{cvitems} % Description(s)
        \item {A data analysis report looking to answer the question of how rates of poverty (poverty headcount ratio) and spending (food expenditures, and non food expenditures) differ based on gender across different African countries.}
        \item{\underline{Skills:} R}
      \end{cvitems}
    }
    
%---------------------------------------------------------
\end{cventries}